Expos\'{e} Master Thesis\\ Rollup System for Layer 2 Scaling

### 2022-12-06 meeting-notes/rollup-system/main.tex
some revisions made

\section{Introduction}
The blockchain systems have grown rapidly in recent years. However, the increased activity has come at a cost to use the network. Many blockchains have reached their capacity limits. The high demand on the network slows down transactions and increases gas prices, so a "scaling solution" is needed and becomes an urgent problem. The main goal of scalability is to increase transaction speed and throughput while ensuring decentralization and security.

@@

Rollups is an off-chain scaling solution, which reduce computational overhead on the mainnet by moving computations and storage out-of-chain to L2. Rollup systems inherit the security of the mainnet by publishing computation results on the chain as shown in Fig~\ref{rollup-batch}. Rollups process a large number of transactions in a rollup batch and then send only  compressed summary data, defines the changes to be made to the state of the mainnet  to L1. This approach allows fixed costs to be spread across multiple transactions in each batch, thus reducing user charges. Rollups therefore provide a significant improvement in transaction throughput.

@@

\section{Design and Implementation of the Rollup System}
In rollup systems, users sign transactions and submit them to an aggregator (sequencer), which checks, orders, and executes these transactions. The aggregator then compresses the data into a rollup batch and publishes the batch as a single transaction on L1. There are two different ways to publish the data to the network. The first approach is optimistic rollup, which assumes that the off-chain transactions are valid and does not require validity proofs for off-chain transactions in the rollup batch. Another approach is zero-knowladge rollup (ZK rollup), in which the aggregator must publish proofs of validity. In contrast, an optimistic rollup responds to a fraud proof to determine where transactions are invalid. After a rollup batch is submitted on L1, anyone can challenge the results of a rollup transaction by computing a fraud proof.

We tend to keep the prototype pure. The implementation contains the core components of a rollup system, but is able to extend the system if we want to enrich it for future research. For security, the system relies on a fraud proof process like in optimistic rollups. A fraud proof is an assertion that a state transition is invalid and therefore the entire batch should be reversed. The system targets the Etherum blockchain, which is the second largest blockchain and seriously suffers from a "scaling problem." The architect of the rollup system is shown in Fig~\ref{rollup-design}.
\begin{figure}[t]
\caption{Design of the rollup system}
\includegraphics[width=12cm]{rollup-design.png}
\centering
\label{rollup-design}
\end{figure}

\subsection{Interacting with the main network}
The operation of the rollup system is controlled by a smart contract deployed on-chain. The L2 system interacts with L1  through the smart contract. The contract receives and process rollup batches. It also stores and  updates the rollup system state (state root), and tracks user deposits. In addition, the contract provides functions to verify rollup batches in the challenge period.

Users must deposit money into the contract before they can use the system. The money is then locked into the contract and the user receives a corresponding amount that can be used in the rollup system.
\subsection{Submitting rollup batches}
The aggregator receives transactions signed and sent by users. In a rollup system, a transaction may come from a user in L2 via a direct peer-to-peer network or from L1 via an intermediate contract running on L1. However, here the rollup system only serves transactions from users in L2. After the aggregator receives the transactions from users, it verifies, orders, and executes them. The aggregator then bundles the off-chain transactions into a rollup batch and sends it to L1 via the smart contract. In this process, the transaction data is compressed and published on-chain as calldata. The published data contains the system state and the transaction batch in a highly compressed form. Since calldata is on-chain as part of the history logs, but is not stored in the smart contract, it is cheaper.

>>>>

\section{Introduction}
Blockchain systems have grown rapidly in recent years. However, the increased activity has come at a cost to the use of the network. Many blockchains have reached their capacity limits. The high demand on the network slows down transactions and increases gas prices, so a "scaling solution" is needed and becomes an urgent problem. The main goal of scalability is to increase transaction speed and throughput while ensuring decentralization and security.

@@

Rollups are an off-chain scaling solution that reduces computational overhead in the main network by moving computation and storage off-chain to L2. Rollup systems inherit the security of the mainnet by publishing computation results on the chain, as shown in Fig~\ref{rollup-batch}. Rollups process a large number of transactions in a rollup batch and then send the compressed summary data defining the changes to the system state to L1. This approach allows fixed costs to be spread across multiple transactions in each rollup batch, reducing user charges. Rollups therefore provide a significant improvement in transaction throughput.

@@

\section{Design and Implementation of a Prototype for Rollup Systems}
In rollup systems, users sign transactions and submit them to an aggregator (sequencer) that checks, orders, and executes these transactions. The aggregator then compresses the data into a rollup batch and compresses the batch with other necessary data (e.g., system state ) into a rollup block and publishes that rollup block as a single transaction on L1. There are two different ways to publish the data to the network. The first approach is optimistic rollup, which assumes that the off-chain transactions are valid and does not require validity proofs for the off-chain transactions in the rollup batch. Another approach is zero-knowladge rollup (ZK rollup), in which the aggregator must publish proofs of validity. In contrast, an optimistic rollup responds to a fraud proof to determine where transactions are invalid. After a rollup batch is submitted to L1, anyone can challenge the results of a rollup transaction by computing a fraud proof.

We tend to keep the prototype pure. The implementation contains only the core components of a rollup system, but is capable of extending the system if we want to enrich it for future research. For security, the system relies on a fraud detection procedure as in optimistic rollups. A fraud proof is an assertion that a state transition is invalid and therefore the entire batch should be reversed. The prototype targets the Etherum blockchain, which is the second largest blockchain and has an urgent "scaling problem." The architect of the prototype rollup system is shown in Fig~\ref{rollup-design}.

\begin{figure}[t]
\caption{Design of the rollup system}
\includegraphics[width=12cm]{rollup-design.png}
\centering
\label{rollup-design}
\end{figure}

\subsection{Interacting with the main network}
The operation of the rollup system is controlled by a smart contract deployed on- chain. The L2 system interacts with L1 through the smart contract. The contract receives and processes rollup blocks. It also stores and updates the status of the rollup system and tracks user deposits. In addition, the contract provides functions to verify rollup batches in the challenge period. Users must deposit money into the smart contract before they can use the system. The money is then locked in the contract and the user receives a corresponding amount that can be used in the rollup system.

\subsection{Submitting rollup batches}
The aggregator receives transactions signed and sent by users. In a rollup system, a transaction may come from a user in L2 via a direct peer-to-peer network or from L1 via an intermediate contract running on L1. However, here the rollup system only serves transactions from users in L2. After the aggregator receives the transactions from users, it verifies, orders, and executes them. The aggregator then bundles the off-chain transactions into a rollup batch and sends it to L1 via the smart contract. In this process, the transaction data is compressed and published on-chain as calldata. The published data contains the system state and the transaction batch in a highly compressed form. Since calldata is on-chain as part of the history logs, but is not stored in the smart contract, it is cheaper.
